### 2023-05-05 main.tex
G symmetric group

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
TO ADD
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.

>>>>

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
 For the sake of notation we denote by 
\begin{equation}
	\begin{split}
		A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
		A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
\begin{equation}\label{cond4A}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
To write its solution we define
\begin{equation}
	\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
\end{equation}
We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
\begin{equation}
	\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
\end{equation}
We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group. \\
The following expression solves \eqref{cond4A}
\begin{equation}
	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
\end{equation}
Indeed
\begin{align}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
\\&+
 A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&=
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&+
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&=
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&=
 	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
\end{align}
where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
\paragraph{Generalization to arbitrary $N$}
For arbitrary $N\geq2$ we have 
\begin{equation}
	\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}
\end{equation}

Thus the explicit expression becomes
\begin{equation}
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
\end{equation}
with the same notation as in $N=3$ case. 
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.
